\begin{thebibliography}{99}

\addcontentsline{toc}{chapter}{Bibliografia}

\bibitem{ANGEL}
E. Angel, D. Shreiner.  Interactive computer graphics: a top-down approach with shader-based OpenGL. Pearson Education, Inc., 6th ed. (2012).

\bibitem{ENGEL}
K. Engel. Real-time volume graphics. A K Peters, Ltd., 1st ed. (2006).

\bibitem{GOMES}
J.M. Gomes, L.C.P R. Velho. Fundamentos da Computa\c{c}\~ao Gr\'afica. Cole\c{c}\~ao Matemática e Aplica\c{c}\~oes. IMPA, 1 ed. (2008).

\bibitem{SHADING}
L. Gritz. Open Shading Language 1.3 - Language Specification, (2013). Disponível em: \url{ https://code.google.com/p/openshadinglanguage/}

\bibitem{MOLLER}
T. A. M\"oller, E. Haines, N. Hoffman. Real-time rendering. A K Peters, Ltd., 3rd ed. (2008).

\bibitem{MUSETH}
 K. Museth. VDB: High-resolution sparse volumes with dynamic topology. ACM Trans. Graph. 32, 3, Article 27. (2013).

\bibitem{SKIENA}
S. S. Skiena. The Algorithm Design Manual. Springer-Verlag London Limited, 2nd ed. (2008).

\bibitem{OCTREE}
Wikipedia - Octree
\url{http://en.wikipedia.org/wiki/Octree}

\bibitem{BPTREE}
Wikipedia - B+ Tree
\url{ http://en.wikipedia.org/wiki/B\%2B_tree}

\end{thebibliography}
\iffalse
1
Open Shading Language 1.3
Language Specification
⃝c Copyright 2009-2013 Sony Pictures Imageworks Inc., et al. All rights reserved.
Editor: Larry Gritz
lg@imageworks.com
Date: 28 Jan, 2013
(with corrections, 15 May, 2013)
URL: https://code.google.com/p/openshadinglanguage/

2
Copyright © 2012, 2009, 2006, 2003, 2000 Pearson Education, Inc., publishing as Addison- Wesley. All rights reserved. Manufactured in the United States of America. 
Library of Congress Cataloging-in-Publication Data
Angel, Edward.
Interactive computer graphics : a top-down approach with shader-based OpenGL /
Edward Angel, David Shreiner. — 6th ed. p. cm.
Includes bibliographical references and index.
ISBN-13: 978-0-13-254523-5 (alk. paper)
ISBN-10: 0-13-254523-3 (alk. paper)
1. Computer graphics. 2. OpenGL. I. Shreiner, Dave. T385.A5133 2012
006.6—dc22

3 	Fundamentos da Computação Gráfica - Edição número 1	
Autor(es):
JONAS DE MIRANDA GOMES
LUIZ CARLOS PACHECO RODRIGUES VELHO
Coleção: Coleção Matemática e Aplicações
ISBN: 978-85-244-0200-5
Código: CMA-06
Data de Publicação: 28/03/2008
Páginas: 603

4 Ken Museth. 2013. VDB: High-resolution sparse volumes with dynamic topology. ACM Trans. Graph. 32, 3, Article 27 (July 2013), 22 pages. DOI=10.1145/2487228.2487235 http://doi.acm.org/10.1145/2487228.2487235

5 Real-time volume graphics / Klaus Engel ... [et al.]. p. cm.
Includes bibliographical references and index. ISBN 13: 978-1-56881-266-3 (alk. paper) ISBN 10: 1-56881-266-3 (alk. paper)
1. Computer graphics. 2. Three-dimensional display systems. I. Engel, Klaus, 1969-

6 http://en.wikipedia.org/wiki/Octree (imagem)

7 http://en.wikipedia.org/wiki/B%2B_tree (imagem)

8 tem uma imagem fora - bem cruel, eu sei... sorry!!

9
Steven S. Skiena
The Algorithm Design Manual Second Edition
Springer-Verlag London Limited 2008

\fi